\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2019-05-23 paper/manuscript_paNote.tex
revising table
discussing dataset contribution

For data availability reasons, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas. The websites were scraped in March 2018. The selection of states and cities is largely dictated by the presence of partisan mayors and availability of the relevant data. Municipal elections in Indiana and Louisiana are partisan across the board, so our sample is primarily focused on these two states. For Indiana and Louisiana, all cities with a website are included, resulting in a considerably larger sample than for the other four states. New York and Washington do not have nominally partisan elections, but for a subset of cities, partisanship can be determined through contribution data (see appendix for more detail). California and Texas contain a number of large cities whose mayors are sufficiently well-known for their partisanship to be available. Our sample is well-balanced on a number of theoretically important dimensions. One, each of the four Census regions are represented with at least one state. Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage. Furthermore, the sample is politically balanced---we have three blue states, and three red states.  The partisan breakdown of city websites is depicted in Table \ref{tab:cityparties}. Details on the sources and methods of raw data collection can be found in the Appendix.

@@

We leverage methods developed in the information retrieval literature to deal with this problem. These boilerplate detection tools are classifiers which rely on both structural features, such as HTML tags, as well as text statistics such as word and sentence length to estimate whether a given portion of an HTML file is useful. We rely on the `boilerpipe' method described in \cite{Kohlschutter2010}, which has been published in a reputable conference, is widely cited, and can easily be implemented through the R package \texttt{boilerpipeR}. The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in Figure \ref{ig:garybp}. We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{lrr}
        \hline
        Process & Software dependency & in \texttt{gov2text} \\
        \hline
        1. Assemble url list. & \texttt{Selenium} & no \\
        2. Collect website files. & \texttt{wget} & no \\
        3. Lemmatize text. & \texttt{spacyr} \citep{spacyr}& yes \\
        4. Remove names. & \texttt{spacyr} & yes \\
        5. Retain nouns, verbs, adjectives. & \texttt{spacyr} & yes \\
        6. Stopword/number/0-2 character word removal. & \texttt{quanteda} \citep{quanteda} & yes \\ 
        7. Retain tokens that are English words. & \texttt{Hunspell} \citep{hunspell} & yes \\
        8. Removal of duplicate documents. & \texttt{gov2text} & yes \\
        \hline
    \end{tabular}
    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.} 
\end{table}

>>>>

For data availability reasons, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas. The websites were scraped in March 2018. The selection of states and cities is largely dictated by the presence of partisan mayors and availability of the relevant data. Municipal elections in Indiana and Louisiana are partisan across the board, so our sample is primarily focused on these two states. For Indiana and Louisiana, all cities with a website are included, resulting in a considerably larger sample than for the other four states. New York and Washington do not have nominally partisan elections, but for a subset of cities, partisanship can be determined through contribution data (see appendix for more detail). California and Texas contain a number of large cities whose mayors are sufficiently well-known for their partisanship to be available. Our sample is well-balanced on a number of theoretically important dimensions. One, each of the four Census regions are represented with at least one state. Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage. Furthermore, the sample is politically balanced---we have three blue states, and three red states.  The partisan breakdown of city websites is depicted in Table \ref{tab:cityparties}. This dataset of city website contents represents a contribution in the growing area of cross-municipality datasets covering local governements \citep[e.g., ][]{marschall2013local,sumner2019}. Details on the sources and methods of raw data collection can be found in the Appendix.

@@

We leverage methods developed in the information retrieval literature to deal with this problem. These boilerplate detection tools are classifiers which rely on both structural features, such as HTML tags, as well as text statistics such as word and sentence length to estimate whether a given portion of an HTML file is useful. We rely on the \texttt{boilerpipe} method described in \cite{Kohlschutter2010}, which is designed to extract blocks of substantive text from websites, and is implemented through the R package \texttt{boilerpipeR}. The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in political science.   The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in Figure \ref{ig:garybp}. We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{lrr}
        \hline
        Process & Software dependency & in \texttt{gov2text} \\
        \hline
        1. Assemble url list. & \texttt{Selenium} & no \\
        2. Collect website files. & \texttt{wget} & no \\
        3. Discard website boilerplate. & \texttt{boilerpipeR} \citep{boilerpipeR} & yes \\
        4. Convert non-HTML files to text. & \texttt{readtext} \citep{readtext} & yes \\
        5. Lemmatize text. & \texttt{spacyr} \citep{spacyr}& yes \\
        6. Remove names. & \texttt{spacyr} & yes \\
        7. Retain nouns, verbs, adjectives. & \texttt{spacyr} & yes \\
        8. Stopword/number removal. & \texttt{quanteda} \citep{quanteda} & yes \\ 
        9. Retain tokens that are English words. & \texttt{Hunspell} \citep{hunspell} & yes \\
        10. Removal of duplicate documents. & \texttt{gov2text} & yes \\
        \hline
    \end{tabular}
    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.} 
\end{table}
